Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an empirical study of the Moran process for the iterated Prisoner's dilemma using reinforcement learning

### 2017-07-10 main.tex
Choose title.
Closes #46

% Title
\title{An Empirical Study of Invasion and Resistance
       for Iterated Prisoner's Dilemma Strategies}
\title{Evolving Invaders and Resistors for the Iterated Prisoner's Dilemma}
\author{Vincent Knight \and
        Marc Harper \and
        Nikoleta E. Glynatsi \and
        Owen Campbell} % TODO Authors?
\date{}

@@

As described in Section~\ref{sec:strong_invaders} the strategies trained with
the payoff maximizing objective are among the best invaders in the library
however they are not as resistant to invasion as the strategies trained using a
Moran objective function. These strategies include trained finite state machine
strategies, but they do not appear to have handshaking mechanisms. Therefore it
is reasonable to conclude that the objective function is the cause of the
emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
handshake for high invasion resistance. TF3 is a better total payoff maximizer
which makes it a better invader along with the strategies
trained to maximize total payoff since successful fitness proportionate selection
is necessary for invasion. Training with an objective with initial population
mix other than $(N/2, N/2)$ may favor invasion or resistance.

>>>>

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an empirical study of the Moran process for the iterated
       Prisoner's dilemma using reinforcement learning}
\author{Vincent Knight \and
        Marc Harper \and
        Nikoleta E. Glynatsi \and
        Owen Campbell} % TODO Authors?
\date{}

@@

As described in Section~\ref{sec:strong_invaders} the strategies trained with
the payoff maximizing objective are among the best invaders in the library
however they are not as resistant to invasion as the strategies trained using a
Moran objective function. These strategies include trained finite state machine
strategies, but they do not appear to have handshaking mechanisms. Therefore it
is reasonable to conclude that the objective function is the cause of the
emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
handshakes for high invasion resistance. TF3 is a better total payoff maximizer
which makes it a better invader along with the strategies
trained to maximize total payoff since successful fitness proportionate selection
is necessary for invasion. Training with an objective with initial population
mix other than $(N/2, N/2)$ may favor invasion or resistance.
